---
title: "black lives matter"
output: html_notebook
---


## Set up working space

typical libraries
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(tidytext)
library(wordcloud2)
library(lubridate)
library(ggwaffle)
```
get data
This weeks tidy tuesday, there are multiple datasets to choose from - firsts and science 
Firsts is the records of african americans breaking the color barrier, science is the achiecements of african americal scientists

```{r}
firsts <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-09/firsts.csv')
head(firsts)
```

 
playing with word clouds

```{r}
# convert accomplishment to text
acc<-firsts %>% 
     select(accomplishment) %>% unnest_tokens(word,accomplishment) %>% 
     anti_join(stop_words) %>% 
     count(word,sort=T) %>% filter(n<400) 
head(acc)
```
I removed the two largest counts to help with visualizing the other words
```{r}
postscript(file='african_american_achievements.jpeg')
wordcloud2(acc, figPath = "/Users/esogin/Desktop/blm.jpg",size = 1.5, color = "#B5D6B2", backgroundColor="#101419")
dev.off()
```

timeline of first accomplishments
```{r}
# floor dates to decades
firsts<-firsts %>% 
          mutate(y=as.Date(as.character(year), format="%Y",origin = lubridate::origin)) %>%
          mutate(decade=floor_date(y,years(20)))
firsts.summary<-firsts %>% group_by(gender, decade) %>% count()
firsts.summary
```
```{r}
waffle_data <- waffle_iron(firsts,sample_size=1,rows=20,aes_d(group = gender))
p1<-ggplot(waffle_data, aes(x, y, fill = group)) + 
  geom_waffle(color='black') + 
  coord_equal() + 
  scale_fill_manual(values=c(c('#586994','#F00699')),name='') + 
  theme_waffle() + ylab('') + xlab('') + theme(legend.position = 'bottom', legend.text = element_text(color='white'))+ 
  theme(plot.background = element_rect(color='black',fill='black'), rect = element_blank()) + 
  ggtitle(label = 'African American firsts by gender',subtitle='') + 
  theme(plot.title=element_text(color='white'))
```


